\section{Experience}

\outerlist {
    \entrybig
    {\textbf{Alaska Satellite Facility}}{University of Alaska Fairbanks, Fairbanks, AK}
    {Student Intern}{September 2022 \textendash Present}
    \innerlist {
        \entry{Sentinel-1 Superseded}
        \entryextra{Created an AWS REST API, DynamoDB database; used SWE principles to create project and integrate it through GitHub actions and Docker using tools such as Jira and GitHub branching to manage issues, goals, and features.}
        \entryextra{The project stores information on data that has been superseded by new data, creating a map where a client can query for a superseded piece of data and get the name of the piece of data that ultimately superseded it.}
    }

    \entrybig
    {\textbf{Personal Projects}}{}
    {}{2018 \textendash Present}
    \innerlist {
        \entry{Multiplicative Persistence}
        \entryextra{Used as a learning excircise with Java to explore computational extremes; both in terms of CPU and memory. Explored concepts such as asynchronous operations, optimization, and OOP.}

        \entry{Arbitrary Precision}
        \entryextra{A necessity of Multiplicative Persistence; storing arbitrarily large integers and decimal values in memory for use in computations, formatting, etc.}

        \entry{Machine Learning Java}
        \entryextra{A neural network and gradient descent algorithm written in Java. Applications of mathematical concepts to programming such as a Calculus, Linear Algebra, and optimization. Also explored Q-learning and Deep learning.}
    }
}